---
title: "Market Basket Analysis"
output: html_notebook
---

## Problem Statement
Consider yourself to be the newly appointed manager of a retail-store ‘ALL-MART’. Your first task as manager of the store is to increase cross-selling


### Objective:

Encourage the customer to buy the items of what they already brought. In order to do this we need to find the association among different items. i.e., If customer buys item `A` how likely he would be buying item `B`. This requires analysis of transactions

**Ex:** Pampers and Beers - During certain period of the day (i.e., during evening) it is identified that people who are buying pampers are also buying beers. So lot of stores separate beers and pampers far away so that people need to walk through the store and can view the products and pick additional products.

```{r}
market_basket <- read.transactions(
  file = '../data/market_basket.csv',
  sep = ',', 
  quote = "",
  format = 'basket', # each record in the file will be treated as transaction
  rm.duplicates = TRUE,
  skip=1
)
```
inspecting first 5 transactions

```{r}
market_basket %>% head(n=5) %>% inspect
```
plot for 10 most frequently brought items
```{r}
itemFrequencyPlot(x = market_basket,
                  topN = 10,
                  type = 'absolute',
                  horiz = TRUE,
                  col = brewer.pal(10,'Spectral'))
```

#### Apirori algorithm 

support = 0.005
confidence = 0.8

```{r}
rule1 <- market_basket %>% apriori(parameter = list(supp = 0.005, conf=0.8)) %>% sort(by = 'confidence')
```

```{r}
summary(rule1)
```

```{r}
rule1 %>% head(n=5)%>% inspect
```

```{r}
rule1 %>% tail(n=5)%>% inspect
```
```{r}
rule1 <- rule1 %>% sort(by='lift')
rule1 %>% head(n=5)%>% inspect
```

```{r}
plot(rule1, engine='htmlwidget')
```

```{r}
plot(rule1, method='two-key', engine='htmlwidget')
```

```{r}
plot(rule1, method='graph', engine='htmlwidget')
```

